Global adjoint tomography -- Model GLAD-M25

### 2018-10-21 main.tex
add Europe setion

{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}
\begin{table}[!htb]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
    \hline
    17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
    40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
    40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
    90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
    \hline
  \end{tabular}\\
  \caption{Changes in fit in the twelve measurement categories
between the new model, GLAD-M25, and its starting model, GLAD-M15, and, in parentheses, between GLAD-M25 and model S362ANI combined with CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
  \label{table:misfit_reduction_M15_M25}
\end{table}

@@

Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
For comparison,
we again include the two global models S362ANI$+$M and S40RTS,
as well as regional model EU60~\citep{zhu2015seismic},
which is based on adjoint tomography.
Again there is good agreemment with the two global models with regards to the longer wavelength structure,
although the Iceland hotspot is less prominent in S362ANI$+$M.
In the 100--200~km depth range we see the Massif Central, the Eiffel hotspot,
and the Central Slovakia Volcanic Field as distinctly slow anomalies,
in agreement with EU60.
In the 400--600~km depth range,
GLAD-M25 is again in good agreement with~EU60,
featuring past subduction in the Mediterranean,
including the present-day Aegean slab.

>>>>

%{\color{red} Wenjie: Make sure the variance reductions are calculated as ln (Phi\_M25 / Phi\_M15).}
%{\color{red} Wenjie: I was using (Phi\_M25 - Phi\_M15) / Phi\_M15. So let me modify it?}
%{\color{blue} Wenjie: yes please. It will only change things slightly, if at all. You need to do the same for Table~\ref{table:misfit_reduction_M15_M25_360}.}

\begin{table}[!htb]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    ~          &  Vertical (\%) & Radial (\%) &  Transverse (\%) \\
    \hline
    %17--40~s  body waves    &   17.4 (31.1)   &       21.1 (37.1) &       24.6 (42.2) \\
    %40--100~s body waves    &   16.8 (31.3)  &       21.3 (40.2)  &       21.7 (42.0) \\
    %40--100~s surface waves &   28.5 (50.1)  &       28.3 (51.1) &       28.4 (53.8)  \\
    %90--250~s surface waves &   14.5 (36.2)  &       13.4 (38.8) &       25.7 (38.6) \\
    17--40~s  body waves    &   19.1 (37.3)   &       23.7 (46.3) &       28.2 (54.8) \\
    40--100~s body waves    &   18.3 (37.5)   &       24.0 (51.4) &       24.5 (54.5) \\
    40--100~s surface waves &   33.6 (69.6)   &       33.3 (71.5) &       33.5 (77.2) \\
    90--250~s all waves &   15.7 (44.9)   &       14.4 (49.1) &       29.6 (48.7) \\
    \hline
  \end{tabular}\\
  \caption{Changes in fit in the twelve measurement categories
  between the new model, GLAD-M25, and its starting model, GLAD-M15,
  and, in parentheses, between GLAD-M25 and model S362ANI combined with
  CRUST2.0, which was the starting model for the GLAD-M15 inversion.}
  \label{table:misfit_reduction_M15_M25}
\end{table}

@@

Fig.~\ref{fig:europe-vs} shows isotropic shear wavespeed perturbations beneath Europe.
For comparison,

In addition to our model GLAD-M25, S362ANI+M and S40RTS, we included a regional
tomography model EU60\citep{zhu2015seismic} into our comparison. The EU60 uses
adjoint methods to iteratively inverse the crust and upper mantle strcuture
beneath the European continent and North Atlantic Ocean, by assimilating
190 earthquakes and 745 seismic station.

Europe is featured by the Trans-European Suture Zone(TESZ), seperating the
Precambrian East Europen Craton(EEC) in the northeast and the Phanerozoic
europe in the southwest.  The TESZ is very consistent across all the models,
even though is much sharper in GLAD-M25 and EU60.

In the north, we observed the high velocity anomaly beneath Central Graben in the
North Sea, and clearly seperated from the EEC bounded at the western north, which is
explained as the lithospheric drip with delamination, as explained in
\cite{zhu2015seismic}.

In the south at the Mediterranean region, the tectonic settings is complex with the
existence of several regional plates. In the west of Mediterranean ocean, there is
Appennines-Maghrebides subductions, with the subduction retreat direction from South
(older, >30Ma)to North(younger, present), with its western border of back-arc basin
following along the coastline of East Spain and South France
\citep{Giordano2017Magmatic}. In our model, this is shown as fast velocity starting
from 400km and extend all the way to the mantle transition zones at 600km beneath the
Mediterranean Ocean, nicely following its west and east boundaries. At shallower depth
such as 100km, we observe low velocity structures, which is explained as the
back-arc extension associated with the roll-back. Compared to S362ANI+M and S40RTS,
our model shows much sharper features for the tectonic structures mentioned above.

Moving furture to the east, at about 400km, there is clearlyfast anomaly lie beneath
the Dinarides Mountains,
sepating the Adria plate and Pannonian Basin and indicating the subudction of Adria
plate into the Euroasian plate. This anomaly get sharper at 600km. The southern
part of it interacts with the Hellenic Arc subductions, which penetrate the mantle
trasition zones and extend below 1,000 kms in our model. We will discuss the Hellenic
Arc in details in the later sections. The Pannonia Basin is featured by low velocity
anomaly at the depth from 100 to 250km, then gradually transferred to high velocity
due to the subduction of Adria plate. The Anatolia plate is shown as slow velocity
anomaly in our model, sharpened from two other global models.

In the Central Europe, there is Cenozoic Ridge System, featured by the low velocity
anomaly, starting from Massif Central and extending to Eifel. Both the EU60 and
GLAD-M25 found slow anomaly lying beneath the northern par of Rhine Graben, explained
as the reservoir that fuels the Eifel hotspot, from 100km to 250km.

In the north of Atlantic Ocean, our model strengthed the slow anlomaly near the
Atlantic Ocean Ridge, especially at the Iceland and Azores. The Iceland, becomes
much strong in our model in the upper mantle from 250km to 400km, compared to
S362ANI+M, extending all the way to the mantle-transition zone. On the other hand,
Azores, is a much shallower hotspot, with the slow anomaly extend at about 250km.
